Hierarchical Reverberation Mapping

### 2013-11-01 Paper/ms.tex
Updated numbers

The marginal posterior distribution for $\mu$ is shown in Figure~\ref{fig:posterior2}
along with the posterior predictive distribution for the ``next'' $\bar{\tau}$ value. The inference about $\mu$ can be summarised as
$\mu = 0.892 \pm 0.033$, and the prediction about $\log_{10}(\bar{\tau})$
may be summarised as $\log_{10}(\bar{\tau}) = 0.892 \pm 0.160$. The Bayesian
approach has clearly separated the uncertainty about $\mu$ from the diversity of the
sample, described by $\sigma$.

>>>>

The marginal posterior distribution for $\mu$ is shown in Figure~\ref{fig:posterior2}
along with the posterior predictive distribution for the ``next'' $\bar{\tau}$ value. The inference about $\mu$ can be summarised as
$\mu = 0.838 \pm 0.047$, and the prediction about $\log_{10}(\bar{\tau})$
may be summarised as $\log_{10}(\bar{\tau}) = 0.838 \pm 0.215$. The Bayesian
approach has clearly separated the uncertainty about $\mu$ from the diversity of the
sample, described by $\sigma$.
